formula1

### 2020-06-07 inst/f1points.Rmd
more work, now have good comparison of points and likelihood ranking

```{r,label=calcpoints}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp
dp <- dp[order(-dp)]
dp[] <- seq_along(dp)
```
now likelihood

```{r,label=calclike}
m <- maxp(H)
m <- sort(m,decreasing=TRUE)
m[] <- seq_along(m)
```

now ranks:

```{r}
jj <- outer(names(m),names(dp),"==")
ox <- dp
oy <- m[which(jj,arr.ind=TRUE)[,1]]
```

and plot:

```{r,label=likevspoints,cache=TRUE,echo=FALSE}
par(pty='s')        # square plot
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

@@

blah blah

>>>>

```{r,label=calcpoints,echo=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
m <- maxp(H)
m <- sort(m,decreasing=TRUE)
m[] <- seq_along(m)
```

```{r,label=likevspoints,cache=TRUE,echo=FALSE}
par(pty='s')        # square plot
ox <- dp
oy <- ordertrans(m,dp)
plot(ox,oy,asp=1,pty='s',xlim=c(0,11.2),ylim=c(0,11.2),pch=16,
    xlab="official order",ylab="my order",main='Formula 1, 2017 season')
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```

@@

```{r,cache=TRUE}
set.seed(1)
f2017 <- read.table("formula1_2017.txt",header=TRUE)[,1:20]
random_table <- rrank(n=ncol(f2017), p=mH)
rownames(random_table) <- colnames(f2017)
Hran <- ordertable2supp(ranktable_to_ordertable(random_table))
m <- maxp(Hran)
sort(m,decreasing=TRUE)
m[] <- seq_along(m)
m
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
dp
ox <- dp
oy <- ordertrans(m,dp)
par(pty="s")
plot(1:10,1:10,asp=1,type="p",pch=NA,
    xlab="official order",ylab="my order",main='Formula 1, 2017 virtual season',
	xlim=c(0,11.2),ylim=c(0,11.2))
points(ox,oy,pch=16)
par(xpd=TRUE)       # allow drivers' names to appear outside plotting region
for(i in seq_along(ox)){text(ox[i],oy[i],names(ox)[i],pos=4,col='gray') }
par(xpd=FALSE)      # stop diagonal line from protruding beyond plotting region
abline(0,1)
```
